Interval Probability for Fuzzy Quantum Theories

### 2016-07-19 prob.tex
prob.tex \subsection{Real-Valued Probability Spaces} updated...

Although specifying a probability for every event looks complex, a
probability measure can be simply constructed by 
\begin{equation}
\pmeas(E)=\sideset{_{\mathbb{R}}}{_{\omega\in E}}\sum\rho(\omega)\textrm{ ,}\label{eq:Radon-Nikodym}
\end{equation}
where $\rho:\Omega\rightarrow[0,1]$ and $\sideset{_{\mathbb{R}}}{_{\omega\in E}}\sum\rho(\omega)=1$.
$\rho$ is called the Radon-Nikodym derivative of $\pmeas$ with respect
to the counting measure, and the Radon-Nikodym theorem states that
the converse is also true.

\begin{thm}{[}Radon-Nikodym theorem for finite probability space~\cite{Nikodym1930,Kolmogorov1950,Folland2013,Swart2013}{]}
For every probability measure~$\pmeas$, there exists an unique Radon-Nikodym
derivative~$\rho$ with respect to the counting measure such that
equation (\ref{eq:Radon-Nikodym}) holds.\qed\end{thm}

>>>>

Although specifying a probability for every event looks complex, a
probability measure can be simply constructed by 
\begin{equation}
\pmeas(E)=\sideset{_{\mathbb{R}}}{_{\omega\in E}}\sum\rho(\omega)\textrm{ ,}\label{eq:Radon-Nikodym}
\end{equation}
where $\rho:\Omega\rightarrow[0,1]$ and $\sideset{_{\mathbb{R}}}{_{\omega\in E}}\sum\rho(\omega)=1$.
$\rho$ is called the Radon-Nikodym derivative of $\pmeas$ with respect
to the counting measure, or just called the Radon-Nikodym derivative
of $\pmeas$ because we are always with respect to the counting measure.
The Radon-Nikodym theorem states that the converse is also true.

\begin{thm}[Radon-Nikodym theorem for finite probability space~\cite{Nikodym1930,Kolmogorov1950,Folland2013,Swart2013}]
For every probability measure~$\pmeas$, there exists an unique Radon-Nikodym
derivative~$\rho$ such that equation~(\ref{eq:Radon-Nikodym})
holds.\qed\end{thm}
